Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-11-29 Craig_revisions/solar_energy_rev1.tex
Updated revisions and letter

Given the diversity of possible planar structures, a vast parameter space exists for their design, and optimization methodologies must
be chosen judiciously.  Drevillon and Ben-Abdallah~\cite{DB_JApplPhys_2007}, as well as Nafzaoui, Drevillon, and Joulain~\cite{NDJ_JApplPhys_2012},
have developed robust optimization 
methodologies that steer multilayer structures to an optimal emissivity profile. The optimum of the emissivity
profile can be defined in a variety of ways with respect to variables including the PV cell and operating conditions.
One such approach for defining such a profile involves using the spectral efficiency of the emitter as a figure-of-merit,
where the spectral efficiency depends on the emissivity of the structure, the band-gap of the PV cell, and the target 
temperature of operation (see section {\it 4.2}).  
The emissivity can be computed from the reflectance
and transmission using the Transfer Matrix Method, enabling efficient computation of the figure-of-merit.  The design problem can then be
formulated as a maximization of the figure-of-merit in terms of the geometry and material properties of the emitter structure.
This approach has been employed to design 1D photonic crystals involving tungsten and dielectric layers with spectral efficiencies of 
about 53\% ~\cite{SKY_JPE_2015} (see Table 2).  Similarly, the Transfer 
Matrix Method can be used to design broad-band absorbers, 
and has led to the prediction of 
absorption efficiencies of 74\% in 1D photonic crystals made of tungsten 
and dielectric layers~\cite{SKY_JPE_2015} (see Table 1).

A different Transfer Matrix Method-based approach for the design of STPV components, recently introduced by us, 
leverages the observation that structures that support perfectly absorbing modes with 
certain characteristics can perform as exceptional selective emitters.  These characteristics, described in detail in
~\cite{FUS_OptExp_2015}, can be
encoded directly into a search routine that allows for the identification of structure geometries that support these modes.  The
optimization over the figure-of-merit is therefore replaced with a search for a zero in T and R, which is equivalent to finding
a zero in the transfer matrix element $M_{2,1}$ under the condition that the transmission is also zero, which can be easily satisfied.
This approach has predicted structures with spectral efficiencies of 68\% at operating temperatures of 1750 K when coupled
with common PV materials~\cite{FUS_OptExp_2015}. The TMM has also been applied by Karalis and Joannopolous to the design of planar emitter/PV cell
systems separated by subwavelength gaps that exploit near-field radiative heat transfer effects, which can exceed the far-field
limit bounded by the Planck blackbody law~\cite{KJ_SciRep_2016}.  In their approach, the dispersions of the planar emitter and PV cell are designed
such that radiative coupling between the two is only allowed at a frequency just above the PV bandgap~\cite{KJ_SciRep_2016}.

@@

\subsection{Design of patterned structures for absorption enhancement using the FDTD method}
Extensions of the previously-discussed multi-layer planar structures involve introducing geometric features in the
lateral dimension(s).  These types of structures include 2D and 3D photonic crystals, metasurfaces, metamaterials, and random-textured materials.
FDTD can be a powerful tool for designing these types of structures, and can be particularly efficient when symmetry and/or periodicity can be
exploited.  Often, these sorts of patterned materials are desired to enhance the absorption of visible light, for example, to design a perfect
absorber across the solar spectrum for solar thermophotovoltaic applications.  For such an application, the transmission, reflection, and
absorption can be computed across the spectrum as features of the surface are varied.  This procedure is illustrated in Figure~\ref{FDTD_Structures} (a) and (b), where the absorptivity of a tungsten surface patterned with pyramidal structures is computed by the FDTD method~\cite{paper1_ref4}. Similarly, Atwater and co-workers
have employed FDTD simulation to design ultra-thin patterned surfaces that behave as broad-band
``super absorbers" capable of enhancing conversion efficiency in
thin-film PV materials~\cite{AFB_NatComm_2011}.  Several of the current authors have utilized FDTD simulations to 
study and
design tungsten absorber surfaces patterned with nanocones 
with absorption efficiencies of 80\%~\cite{me1} (see Table 1),
as well as tungsten blazed grating emitter surfaces with spectral efficiencies of 59\%~\cite{me2} (see Table 2).

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the spectral efficiency which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

@@

\textcolor{black}{By transforming the incoming solar radiation from a broad-band source to a more narrow-band one, STPV systems can operate at efficiencies exceeding the Shockley-Queisser limit of 29\% for silicon PV cells operating under diffuse radiation~\cite{scranton_from_gupta}.  This is due to the fact that the major factors that drive the Shockley-Queisser limit are losses due to below-bandgap radiation and thermalization, which are both dependent on the spectrum of light illuminating the PV cell~\cite{SQ}.  By efficiently altering the spectrum of light reaching the PV cell, the system efficiency can be increased.  In fact, the upper {\it theoretical} limit for STPV system efficiency is 85.4\%~\cite{A2}.  While reference \cite{RF_OptExp_2009} and \cite{global_opt} used many idealities, they clearly show that STPV systems are capable of having efficiencies above the Shockley-Queisser limit for single junction PV cells.  Detailed balance calculations support this conclusion as well~\cite{g5}.}

\begin{table}
	\caption{Efficiency, relative solar absorption, and relative thermal emission at a temperature of 1700 K of selected absorbing surfaces.}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper,nnnNature}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{Palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

The absorbing surfaces for STPV devices are similar to those used in ST systems, although higher operating temperatures (up to around 1750 K) 
make thermal stability a more prominent concern, and high levels of solar concentration (\textgreater4000) make a high $\alpha_{sol}$ of 
paramount concern.  This means that nanotextured absorbing surfaces are a very good match for these systems.  Most experimental STPV systems 
to date have utilized blackbody absorbing surfaces \cite{exp_tokyo,exp_madrid,exp_russia,MIT_paper}, leaving room for much improvement by using 
selective absorbing surfaces. Recent results have reported record efficiencies~\cite{g11,SKY_JPE_2015} using both 
selective absorbers and selective emitters. A yttria-stabilized zirconia and tungsten stack was used as a selective absorber in an experimental system~\cite{SKY_JPE_2015}, 
but while it's thermal emission was low, its performance was hindered by a low $\alpha_{sol}$ of 80\%.  Simulations of various surfaces 
have shown large gains in system efficiency from the use of nanotextured selective, such as pseudo-random 
nanocones with an $\alpha_{sol}$ of 97\% and $\epsilon_{abs}$ of 16\% \cite{me1}, or pyramidal nanostructures in tungsten 
with an $\alpha_{sol}$ of 92\% and $\epsilon_{abs}$ of 13\% \cite{paper1_ref4} but none have been experimentally 
demonstrated in a working STPV system to date \cite{paper1_ref5,paper1_ref6}.

@@

Table \ref{abs_eff_table} shows the $\alpha_{sol}$ and $\epsilon_{abs}$ of some absorbing surfaces, as well as a calculated surface efficiency.  The quantity $\eta_{abs}$ is given by
\begin{align}
\label{overall_sss_eq}\eta_{abs}(T)& = \frac{\int_{0}^{\infty}\left\{E_{inc}(\lambda)\alpha(\lambda)-\epsilon(\lambda)B(\lambda,T)\right\}d\lambda}{\int_{0}^{\infty}E_{inc}(\lambda)d\lambda}\\
\label{e_incident}E_{inc}(\lambda) &= C \: \eta_{conc} \: E_{sun}(\lambda),
\end{align}
where $\alpha(\lambda)$ is the spectral absorption of the surface, $\epsilon(\lambda)$ is the spectral emittance of the surface, $C$ is the concentration ratio of incoming sunlight, 
$\eta_{conc}$ is the solar concentration efficiency, $E_{sun}(\lambda)$ is the 
spectral irradiance of the sun at the earth's surface, $B(\lambda, T)$ is 
Planck's law for blackbody radiation, and $E_{inc}(\lambda)$ is the spectral 
energy incident on the absorbing surface.

For emitting surfaces, a similar approach to absorbing surfaces can be taken, but with a focus on low reflectance in a narrow peak near a specific wavelength (which depends on the bandgap energy of the PV cell used), as opposed to a broad low reflectance band in the visible region.  To accurately compare emitting surfaces, their spectral efficiency is used.

The spectral efficiency is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
SE = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral emissivity of the emitting surface, approximated as the surface's absorptivity.  \textcolor{black}{This gives the relative efficiency of the emitting surface, but does not represent an overall system efficiency.  Specifically, this equation does not take into account the fill factor, open-circuit voltage, recombination losses within the PV cell, or any non-idealities in the STPV system.  The values obtained from this equation do not represent real or even potential system efficiencies, but serve as a convenient way to compare the performance of various surfaces as well as a tool for optimization.  While PV cells with external quantum efficiencies that vary by wavelength could change the optimum bandgap stated by this equation, the effect is generally small and would need to be evaluated on a case by case basis.}

@@

\begin{table}
	\caption{Optical efficiency of selected emitting surfaces at 1700 K~\cite{me_thesis}.}
	\label{FOM_table}
	\begin{center}
		\begin{tabular}{|lc|}
			\hline
			Emitter type & $\eta_{emit}$\\
			\hline	
			Ideal emitting surface & 0.84 \\
			Periodic hole array on W & 0.64 (simulated)\\
			Blazed grating on W & 0.59 ~\cite{me2} \\
			Anti-reflection coating on W & 0.59 (simulated) \\
			Complex square grating on W & 0.53~\cite{paper2_ref14}\\
			1-D photonic crystal on W & 0.53~\cite{SKY_JPE_2015}\\
			Micro-cavity in W & 0.51~\cite{paper2_ref6} \\
			{A}l$_2${O}$_3$/{E}r$_3${A}l$_5${O}$_{12}$ eutectic composite & 0.41~\cite{exp_tokyo}\\
			Blackbody emitter & 0.29\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\textcolor{black}{Many nanotextured emitting structures have been simulated to be extremely efficient \cite{paper2_ref13}.  These include blazed gratings on tungsten \cite{me2}, complex square gratings on tungsten \cite{paper2_ref14}, micro-cavities in tungsten \cite{paper2_ref6}, tungsten surface gratings \cite{paper1_ref6}, 3-D photonic crystals \cite{paper2_ref10}, and metamaterials \cite{meta}.  Table \ref{FOM_table} shows the spectral efficiencies of some of these surfaces.  This shows a large increase in efficiency for selective emitters over blackbody emitters.  While experimental systems using these structures have not yet been realized, they promise large efficiency gains for the future.  Table \ref{STPV_sys_table} shows the electrical efficiencies of some simulated and experimental STPV systems. These efficiencies are for systems operating under AM1.5 solar simulators or real-world solar conditions.  They all are converting solar energy to usable electrical energy (work).}

The simulations outlined here show a large difference in predicted efficiency; however, a significant portion of this variation is caused by simulation parameters.  Since there is no standard for simulated STPV systems, some papers use an ideal model where only losses due to the surfaces are accounted for, while others use a more realistic model that encompasses many losses.  Namely, references \cite{RF_OptExp_2009} and \cite{global_opt} assume ideal PV cells, ideal solar concentrators, and assume an ideal view-factor between the emitting surface and solar cells.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} attempt to model PV cell losses and realistic absorbing and emitting surfaces.  Some of the remaining difference between efficiencies in the modeled systems is also due to differences in assumptions between simulations.

>>>>

Given the diversity of possible planar structures, a vast parameter space exists for their design, and optimization methodologies must
be chosen judiciously.  Drevillon and Ben-Abdallah~\cite{DB_JApplPhys_2007}, as well as Nafzaoui, Drevillon, and Joulain~\cite{NDJ_JApplPhys_2012},
have developed robust optimization 
methodologies that steer multilayer structures to an optimal emissivity profile. The optimum of the emissivity
profile can be defined in a variety of ways with respect to variables including the PV cell and operating conditions.
One such approach for defining such a profile involves using the ultimate efficiency of the emitter as a figure-of-merit,
where the ultimate efficiency depends on the emissivity of the structure, the band-gap of the PV cell, and the target 
temperature of operation (see section {\it 4.2}).  
The emissivity can be computed from the reflectance
and transmission using the Transfer Matrix Method, enabling efficient computation of the figure-of-merit.  The design problem can then be
formulated as a maximization of the figure-of-merit in terms of the geometry and material properties of the emitter structure.
This approach has been employed to design 1D photonic crystals involving tungsten and dielectric layers with ultimate efficiencies of 
about 53\% ~\cite{SKY_JPE_2015} (see Table 2).  Similarly, the Transfer 
Matrix Method can be used to design broad-band absorbers, 
and has led to the prediction of 
absorption efficiencies of 74\% in 1D photonic crystals made of tungsten 
and dielectric layers~\cite{SKY_JPE_2015} (see Table 1).

A different Transfer Matrix Method-based approach for the design of STPV components, recently introduced by us, 
leverages the observation that structures that support perfectly absorbing modes with 
certain characteristics can perform as exceptional selective emitters.  These characteristics, described in detail in
~\cite{FUS_OptExp_2015}, can be
encoded directly into a search routine that allows for the identification of structure geometries that support these modes.  The
optimization over the figure-of-merit is therefore replaced with a search for a zero in T and R, which is equivalent to finding
a zero in the transfer matrix element $M_{2,1}$ under the condition that the transmission is also zero, which can be easily satisfied.
This approach has predicted structures with ultimate efficiencies of 68\% at operating temperatures of 1750 K when coupled
with common PV materials~\cite{FUS_OptExp_2015}. The TMM has also been applied by Karalis and Joannopolous to the design of planar emitter/PV cell
systems separated by subwavelength gaps that exploit near-field radiative heat transfer effects, which can exceed the far-field
limit bounded by the Planck blackbody law~\cite{KJ_SciRep_2016}.  In their approach, the dispersions of the planar emitter and PV cell are designed
such that radiative coupling between the two is only allowed at a frequency just above the PV bandgap~\cite{KJ_SciRep_2016}.

@@

\subsection{Design of patterned structures for absorption enhancement using the FDTD method}
Extensions of the previously-discussed multi-layer planar structures involve introducing geometric features in the
lateral dimension(s).  These types of structures include 2D and 3D photonic crystals, metasurfaces, metamaterials, and random-textured materials.
FDTD can be a powerful tool for designing these types of structures, and can be particularly efficient when symmetry and/or periodicity can be
exploited.  Often, these sorts of patterned materials are desired to enhance the absorption of visible light, for example, to design a perfect
absorber across the solar spectrum for solar thermophotovoltaic applications.  For such an application, the transmission, reflection, and
absorption can be computed across the spectrum as features of the surface are varied.  This procedure is illustrated in Figure~\ref{FDTD_Structures} (a) and (b), where the absorptivity of a tungsten surface patterned with pyramidal structures is computed by the FDTD method~\cite{paper1_ref4}. Similarly, Atwater and co-workers
have employed FDTD simulation to design ultra-thin patterned surfaces that behave as broad-band
``super absorbers" capable of enhancing conversion efficiency in
thin-film PV materials~\cite{AFB_NatComm_2011}.  Several of the current authors have utilized FDTD simulations to 
study and
design tungsten absorber surfaces patterned with nanocones 
with absorption efficiencies of 80\%~\cite{me1} (see Table 1),
as well as tungsten blazed grating emitter surfaces with ultimate efficiencies of 59\%~\cite{me2} (see Table 2).

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the ultimate efficiency which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

@@

\textcolor{red}{By transforming the incoming solar radiation from a broad-band source to a more narrow-band one, STPV systems can operate at efficiencies exceeding the Shockley-Queisser limit of 29\% for silicon PV cells~\cite{scranton_from_gupta}, or the higher Shockley-Queisser limit of 40.8\% for a single-junction PV cell with an optimized bandgap~\cite{opt_BG}.}  This is due to the fact that the major factors that drive the Shockley-Queisser limit are losses due to below-bandgap radiation and thermalization, which are both dependent on the spectrum of light illuminating the PV cell~\cite{SQ}.  By efficiently altering the spectrum of light reaching the PV cell, the system efficiency can be increased.  In fact, the upper {\it theoretical} limit for STPV system efficiency is 85.4\%~\cite{Therm_stabil_W_microstructures}.  While reference \cite{RF_OptExp_2009} and \cite{global_opt} used many idealities, they clearly show that STPV systems are capable of having efficiencies above the Shockley-Queisser limit for single junction PV cells.  Detailed balance calculations support this conclusion as well~\cite{g5}.

\begin{table}
	\caption{\textcolor{red}{Absorber efficiency corresponding to equation \ref{overall_sss_eq}, relative solar absorption, and relative thermal emission at a temperature of 1700 K and a concentration factor of 2500 for selected absorbing surfaces.}}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper,nnnNature}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{Palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

The absorbing surfaces for STPV devices are similar to those used in ST systems, although higher operating temperatures (up to around 1750 K) 
make thermal stability a more prominent concern, and high levels of solar concentration (\textgreater4000) make a high $\alpha_{sol}$ of 
paramount concern.  This means that nanotextured absorbing surfaces are a very good match for these systems.  Most experimental STPV systems 
to date have utilized blackbody absorbing surfaces \cite{exp_tokyo,exp_madrid,exp_russia,MIT_paper}, leaving room for much improvement by using 
selective absorbing surfaces. Recent results have reported record efficiencies~\cite{g11,SKY_JPE_2015} using both 
selective absorbers and selective emitters. A yttria-stabilized zirconia and tungsten stack was used as a selective absorber in an experimental system~\cite{SKY_JPE_2015}, 
but while it's thermal emission was low, its performance was hindered by a low $\alpha_{sol}$ of 80\%.  Simulations of various surfaces 
have shown large gains in system efficiency from the use of nanotextured selective, such as pseudo-random 
nanocones with an $\alpha_{sol}$ of 97\% and $\epsilon_{abs}$ of 16\% \cite{me1}, or pyramidal nanostructures in tungsten 
with an $\alpha_{sol}$ of 92\% and $\epsilon_{abs}$ of 13\% \cite{paper1_ref4} but none have been experimentally 
demonstrated in a working STPV system to date.

@@

Table \ref{abs_eff_table} shows the $\alpha_{sol}$ and $\epsilon_{abs}$ of some absorbing surfaces, as well as a calculated surface efficiency.  The quantity $\eta_{abs}$ is given by
\begin{align}
\label{overall_sss_eq}\eta_{abs}(T)& = \frac{\int_{0}^{\infty}\left\{E_{inc}(\lambda)\alpha(\lambda)-\epsilon(\lambda)B(\lambda,T)\right\}d\lambda}{\int_{0}^{\infty}E_{inc}(\lambda)d\lambda}\\
\label{e_incident}E_{inc}(\lambda) &= C \: E_{sun}(\lambda),
\end{align}
where $\alpha(\lambda)$ is the spectral absorption of the surface, $\epsilon(\lambda)$ is the spectral emittance of the surface,\textcolor{red}{ $C$ is the concentration factor of incoming sunlight, including concentrator ratio and concentrator efficiency,} $E_{sun}(\lambda)$ is the 
spectral irradiance of the sun at the earth's surface, $B(\lambda, T)$ is 
Planck's law for blackbody radiation, and $E_{inc}(\lambda)$ is the spectral 
energy incident on the absorbing surface.

For emitting surfaces, a similar approach to absorbing surfaces can be taken, but with a focus on low reflectance in a narrow peak near a specific wavelength (which depends on the bandgap energy of the PV cell used), as opposed to a broad low reflectance band in the visible region.  To accurately compare emitting surfaces, their ultimate efficiency is used.

The ultimate efficiency is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
SE = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral emissivity of the emitting surface, approximated as the surface's absorptivity.  \textcolor{black}{This gives the relative efficiency of the emitting surface, but does not represent an overall system efficiency.  Specifically, this equation does not take into account the fill factor, open-circuit voltage, recombination losses within the PV cell, or any non-idealities in the STPV system.  The values obtained from this equation do not represent real or even potential system efficiencies, but serve as a convenient way to compare the performance of various surfaces as well as a tool for optimization.  While PV cells with external quantum efficiencies that vary by wavelength could change the optimum bandgap stated by this equation, the effect is generally small and would need to be evaluated on a case by case basis.}

@@

\begin{table}
	\caption{Ultimate efficiency of selected emitting surfaces at 1700 K and a bandgap of 0.72 eV~\cite{me_thesis}.}
	\label{FOM_table}
	\begin{center}
		\begin{tabular}{|lc|}
			\hline
			Emitter type & $\eta_{emit}$\\
			\hline	
			Ideal emitting surface & 0.84 \\
			Periodic hole array on W & 0.64 (simulated)\\
			Blazed grating on W & 0.59 ~\cite{me2} \\
			Anti-reflection coating on W & 0.59 (simulated) \\
			Complex square grating on W & 0.53~\cite{paper2_ref14}\\
			1-D photonic crystal on W & 0.53~\cite{SKY_JPE_2015}\\
			Micro-cavity in W & 0.51~\cite{paper2_ref6} \\
			{A}l$_2${O}$_3$/{E}r$_3${A}l$_5${O}$_{12}$ eutectic composite & 0.41~\cite{exp_tokyo}\\
			Blackbody emitter & 0.29\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\textcolor{black}{Many nanotextured emitting structures have been simulated to be extremely efficient \cite{paper2_ref13}.  These include blazed gratings on tungsten \cite{me2}, complex square gratings on tungsten \cite{paper2_ref14}, micro-cavities in tungsten \cite{paper2_ref6}, tungsten surface gratings \cite{paper1_ref6}, 3-D photonic crystals \cite{paper2_ref10}, and metamaterials \cite{meta}.  Table \ref{FOM_table} shows the ultimate efficiencies of some of these surfaces.  This shows a large increase in efficiency for selective emitters over blackbody emitters.  While experimental systems using these structures have not yet been realized, they promise large efficiency gains for the future.  Table \ref{STPV_sys_table} shows the electrical efficiencies of some simulated and experimental STPV systems. These efficiencies are for systems operating under AM1.5 solar simulators or real-world solar conditions.  They all are converting solar energy to usable electrical energy (work).}

The simulations outlined here show a large difference in predicted efficiency; however, a significant portion of this variation is caused by simulation parameters.  Since there is no standard for simulated STPV systems, some papers use an ideal model where only losses due to the surfaces are accounted for, while others use a more realistic model that encompasses many losses.  Namely, references \cite{RF_OptExp_2009} and \cite{global_opt} assume ideal PV cells, ideal solar concentrators, and assume an ideal view-factor between the emitting surface and solar cells.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} attempt to model PV cell losses and realistic absorbing and emitting surfaces.  Some of the remaining difference between efficiencies in the modeled systems is also due to differences in assumptions between simulations.  \textcolor{red}{Additional technical challenges associated with STPV and TPV systems that are not included in any of the aforementioned studies include the high resistance losses associated with large current outputs form PV cells, and the large amount of cooling necessary to hold the PV cells at adequate temperatures.  While the use of selective emitters does significantly reduce the thermal load on the PV cells, active cooling will still be necessary for systems which utilize a high level of solar concentration.  The power required for this cooling is not taken into account in the efficiency numbers outlined in this review.}
